---
theme-settings:
  theme: default
  barposition: top
  footer-left: 'Made with [surveydown](https://surveydown.org)'
  footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/fhdsl/anvil_surveys/tree/sota2026)'

survey-settings:
  mode: preview
  show-previous: true
  start-page: welcome
  use-cookies: false #update after building
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: false
  all-shuffled: false
  required:
    - role
    - institution_affil
    - team_member
    - user_description
    
system-messages:
  cancel: Cancel
  confirm-exit: Confirm Exit
  sure-exit: Are you sure you want to exit the survey?
  submit-exit: Submit and Exit
  warning: Warning
  required: Please answer all required questions before proceeding.
  rating-title: Before you go...
  rating-text: 'Rate your survey experience:'
  rating-scale: from 1-poor to 5-excellent
  previous: Previous
  next: Next
  exit: Exit Survey
  close-tab: Please close this tab manually to exit the survey.
  choose-option: Choose an option...
  click: Click here
  redirect: Redirecting in
  seconds: seconds
  new-tab: Opens in a new tab
  redirect-error: "Error: This text won't trigger any redirection..."
---

```{r}
library(surveydown)
```

--- welcome

# State of the AnVIL 2026

<!-- include logo -->

Add background info on the poll

```{r}

sd_nav(page_next = "page2", show_previous = FALSE)
```

--- screenout

## Thank you for your interest!

Unfortunately, you do not meet the eligibility requirements for this survey.

```{r}
sd_close()
```

--- page2

<!-- Demographics -->

```{r}

sd_question(
  type   = 'mc',
  id     = 'role',
  label  = 'What is your career stage/position?',
  option = c(
    'Student (undergraduate, graduate, or medical)' = 'student',
    'Postdoc' = 'postdoc',
    'Academic (professor or principal investigator)' = 'academic',
    'Service (staff scientist, research assistant, bioinformatician, program administrator)' = 'service',
    'Other' = 'other'
  )
)

sd_question(
  type   = 'text',
  id     = 'role_other',
  label  = 'Please describe your "Other" career stage/position.'
)

sd_question(
  type   = 'mc',
  id     = 'institution_affil',
  label  = 'What type of institution are you affiliated with?',
  option = c(
    'Research Intensive Institution' = 'research',
    'Teaching Focused Institution' = 'teaching',
    'Hospital/Medical Center or School' = 'clinical',
    'Government' = 'gov',
    'Industry' = 'industry',
    'Other' = 'other'
  )
)

sd_question(
  type   = 'text',
  id     = 'institution_affil_other',
  label  = 'Please describe your "Other" institutional affiliation.'
)

sd_question(
  type   = 'mc',
  id     = 'team_member',
  label  = 'Are you currently part of the AnVIL Internal Team?',
  option = c(
    'Yes' = 1, #skip to page 4
    'No'  = 0 #send to next question
  )
)

sd_question(
  type   = 'mc',
  id     = 'user_description',
  label  = 'Which statement best describes your awareness and current usage of the AnVIL Platform?',
  option = c(
    'I currently use AnVIL for my work/research.' = 'aware_current', #send to next page (No skip logic)
    'I have explored or trained on AnVIL, but have not used it for my work/research.' = 'aware_explore', #send to page 3b
    'I have previously used AnVIL for my work/research, but do not currently.' = 'aware_previous', #send to page 3b
    'I have heard of AnVIL, but never used it.' = 'aware_unused', #send to page 3b
    'I have never heard of AnVIL.' = 'unaware' #send to page 3b
  )
)
```

--- page3a

<!-- ## Current / General Users -->

This section asks some general questions about your use of AnVIL.

```{r}

sd_question(
  type   = 'mc_multiple',
  id     = 'why_external',
  label  = 'Do any of the following factor into your use of AnVIL? (select all that apply)',
  option = c(
    'My consortium uses AnVIL' = 'consortium',
    'My institution or funder requires it' = 'required',
    "I use it to comply with NIH's Data security policies" = 'dms',
    'My institution supports or encourages its use' = 'institutional_support',
    'None of these' = 'none'
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'why_description',
  label  = 'Why do you choose to use AnVIL? (select all that apply)',
  option = c(
    'To collaborate with others' = 'collab',
    'To make my work more transparent or reproducible' = 'reproducibility',
    'I tried it and it met my needs' = 'tried_liked',
    'It offers features I need (e.g., data access, tools, workflows, computing resources)' = 'specific_feat',
    'Recommended by colleagues' = 'community_rec',
    'It is more affordable than other options' = 'affordability',
    'Other' = 'other'
  )
)

sd_question(
  type   = 'textarea',
  id     = 'why_description_other',
  label  = 'Please describe your "Other" reason for using AnVIL.'
)

sd_question( ### <-- WHAT DO WE HOPE TO LEARN
  type   = 'mc',
  id     = 'consortia_analysis',
  label  = 'Does your consortium run analyses with AnVIL?',
  option = c(
    'Yes' = 1,
    'No' = 0
  )
)

sd_question( ### <-- WHAT DO WE HOPE TO LEARN
  type   = 'mc',
  id     = 'consortia_data',
  label  = 'Does your consortium use AnVIL to store or release data?',
  option = c(
    'Yes' = 1,
    'No'  = 0
  )
)

sd_question( ### <-- WHAT DO WE HOPE TO LEARN
  type  = 'text',
  id    = 'consortia_affil',
  label = 'Please list your relevant consortia affiliations.'
)

sd_question(
  type   = 'mc',
  id     = 'length_of_use',
  label  = 'How long have you been using AnVIL?',
  option = c(
    '< 1 year' = '0',
    '1-2 years' = '1_2',
    '2-4 years' = '2_4',
    '4-6 years' = '4_6',
    '6+ years' = '6'
  )
)

sd_question(
  type   = 'mc',
  id     = 'nps_score',
  label  = 'On a scale of 0–10, how likely are you to recommend AnVIL to a colleague or collaborator?',
  option = c(
    '0 - Not at all likely' = 0,
    '1' = 1, 
    '2' = 2, 
    '3' = 3, 
    '4' = 4, 
    '5' = 5,
    '6' = 6, 
    '7' = 7, 
    '8' = 8, 
    '9' = 9,
    '10 - Extremely likely' = 10
  )
)

sd_question(
  type  = 'text',
  id    = 'nps_score_explain',
  label = '(Optional) Tell us what factored into your response above.'
)

sd_nav(page_next = 'page4')
```

--- page3b

<!-- ## Previous Users -->

```{r}

sd_question(
  type   = 'mc_multiple',
  id     = 'why_stopped',
  label  = 'Why did you stop using AnVIL? (select all that apply)',
  option = c(
    'My project or role changed' = 'project_change',
    'It no longer met my needs' = 'unmet_needs',
    'I found a different tool or platform that works better for me' = 'switched',
    'Cost' = 'cost',
    'Technical or usability issues' = 'technical',
    'Lack of institutional or funder support' = 'lack_support',
    'Other' = 'other'
  )
)

sd_question(
  type   = 'textarea',
  id     = 'why_stopped_other',
  label  = 'Please describe the "Other" reason you stopped using AnVIL.'
)

sd_question(
  type   = 'mc_multiple',
  id     = 'what_would_help_previous',
  label  = 'What would make AnVIL easier or more useful for your work? (select all that apply)',
  option = c(
    'Clearer documentation or tutorials' = 'documentation',
    'A simpler or more intuitive interface' = 'usability',
    'Lower cost / more funding' = 'cost',
    'Institutional admin / IT support' = 'institutional',
    'Access to additional datasets' = 'data_access',
    'Access to additional tools or workflows' = 'tools_workflows',
    'More training or onboarding resources' = 'training',
    'Better integration with other platforms I use' = 'integration',
    "Nothing - I don't need AnVIL right now" = 'no_need',
    'Nothing — AnVIL already meets my needs' = 'all_met',
    'None of these' = "none",
    'Other' = 'other'
  )
)

sd_question(
  type   = 'textarea',
  id     = 'what_would_help_previous_other',
  label  = 'Please describe "Other" that would make AnVIL easier or more useful for your work.'
)

sd_question(
  type   = 'matrix',  # or mc_multiple??
  id     = 'platform_priorities_previous',
  label  = 'When choosing a computing platform for your work, how important are the following?',
  row = c(
    'Access to relevant datasets' = 'data_access',
    'Cost' = 'cost',
    'Ease of use / learning curve' = 'usability',
    'Security and compliance (e.g., controlled-access data)' = 'security',
    'Computing power or scalability' = 'compute_power',
    'Availability of pre-built tools or workflows' = 'tools_workflows',
    'Ability to collaborate with others' = 'collaboration',
    'Institutional admin / IT support' = 'institutional',
    'Community or peer support' = 'community'
  ),
  option = c(
    "Not a priority" = 1,
    "Low priority" = 2,
    "Moderate priority" = 3,
    "High priority" = 4,
    "Essential" = 5
  )
)

sd_nav(page_next = 'end')
```

--- page3c

<!-- ## Potential Users -->

```{r}

## Might need to be different for never heard of it. Eg, what is important in a computing platform?
sd_question(
  type   = 'mc_multiple',
  id     = 'what_would_help_potential',
  label  = 'What would make AnVIL easier or more useful for your work? (select all that apply)',
  option = c(
    'Clearer documentation or tutorials' = 'documentation',
    'A simpler or more intuitive interface' = 'usability',
    'Lower cost / more funding' = 'cost',
    'Institutional admin / IT support' = 'institutional',
    'Access to additional datasets' = 'data_access',
    'Access to additional tools or workflows' = 'tools_workflows',
    'More training or onboarding resources' = 'training',
    'Better integration with other platforms I use' = 'integration',
    "Nothing - I don't need AnVIL right now" = 'no_need',
    'None of these' = "none",
    'Other' = 'other'
  )
)

sd_question(
  type   = 'textarea',
  id     = 'what_would_help_potential_other',
  label  = 'Please describe "Other" that would make AnVIL easier or more useful for your work.'
)

sd_question(
  type   = 'matrix',  # or mc_multiple??
  id     = 'platform_priorities_potential',
  label  = 'When choosing a computing platform for your work, how important are the following?',
  row = c(
    'Access to relevant datasets' = 'data_access',
    'Cost' = 'cost',
    'Ease of use / learning curve' = 'usability',
    'Security and compliance (e.g., controlled-access data)' = 'security',
    'Computing power or scalability' = 'compute_power',
    'Availability of pre-built tools or workflows' = 'tools_workflows',
    'Ability to collaborate with others' = 'collaboration',
    'Institutional admin / IT support' = 'institutional',
    'Community or peer support' = 'community'
  ),
  option = c(
    "Not a priority" = 1,
    "Low priority" = 2,
    "Moderate priority" = 3,
    "High priority" = 4,
    "Essential" = 5
  )
)

sd_nav(page_next = 'end')
```

--- page4

**The next sets of questions ask specifically how you tend to use AnVIL**.

## Specific Use: Data submission

```{r}

sd_question(
  type   = 'mc',
  id     = 'use_submit_data',
  label  = 'Do you submit or manage data (e.g., for a consortium or lab)?',
  option = c(
    'Yes' = 1,
    'No' = 0,
    'Unsure' = 99 #don't ask about anything
  )
)

sd_question(
  type   = 'mc',
  id     = 'use_submit_raw_summarized',
  label  = 'Do you submit or manage raw data (e.g., sequencing reads) or summarized data (e.g., count tables, variant calls, etc.)?',
  option = c(
    'Raw data' = 'raw',
    'Summarized data' = 'summarized',
    'Both raw and summarized data' = 'both',
    'Unsure' = 'unsure'
  )
)

sd_question(
  type   = 'mc',
  id     = 'use_submit_satisfaction',
  label  = 'How satisfied are you with AnVIL data submission or management?',
  option = c(
    'Very dissatisfied' = 1,
    'Dissatisfied' = 2,
    'Neutral' = 3,
    'Satisfied' = 4,
    'Very satisfied' = 5
  )
)

sd_question( ## Rephrase?
  type   = 'textarea',
  id     = 'what_would_help_submit',
  label  = 'What would make AnVIL easier or more useful **for your data submission or management work**?'
)

sd_nav(page_next = 'page5')
```

--- page5

## Specific Use: Group support

```{r}

sd_question(
  type   = 'mc',
  id     = 'use_support',
  label  = 'Do you perform group support tasks (e.g., managing or tracking billing)?',
  option = c(
    'Yes' = 1,
    'No' = 0
  )
)

sd_question(
  type = 'mc',
  id   = 'use_support_satisfaction',
  label  = 'How satisfied are you with your support tasks on AnVIL?',
  option = c(
    'Very dissatisfied' = 1,
    'Dissatisfied' = 2,
    'Neutral' = 3,
    'Satisfied' = 4,
    'Very satisfied' = 5
  )
)
#standardize throughout that if 1 is good, it's good everywhere <-- isn't 1 usually "worst"?

sd_question( ## Rephrase?
  type   = 'textarea',
  id     = 'what_would_help_use_support',
  label  = 'What would make **your support tasks on AnVIL** easier or more useful?'
)

sd_nav(page_next = 'page6')
```

--- page6

## Specific Use: Running analyses

```{r}

sd_question(
  type   = 'mc',
  id     = 'use_interactive',
  label  = 'Do you run interactive analyses (e.g., using Galaxy in AnVIL, Jupyter Notebooks, RStudio)?',
  option = c(
    'Yes' = 1,
    'No' = 0,
    'Unsure' = 99
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'which_interactive_use_anvil',
  label  = 'Which interactive analysis solutions do you utilize **on the AnVIL**? (select all that apply)',
  option = c(
    'Jupyter Notebooks / terminal' = 'jupyter_notebooks',
    'RStudio' = 'rstudio',
    'Galaxy in AnVIL' = 'galaxy'
  )
)

sd_question(
  type   = 'textarea',
  id     = 'which_interactive_use_separate',
  label  = 'Which interactive analysis solutions do you utilize **separate from the AnVIL**?',
)

sd_question(
  type   = 'mc',
  id     = 'use_workflows',
  label  = 'Do you run scalable workflows (e.g., WDL)?',
  option = c(
    'Yes' = 1,
    'No' = 0,
    'Unsure' = 99
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'whose_data_use',
  label  = 'Do you bring your own data to the AnVIL or use AnVIL hosted datasets? (select all that apply)',
  option = c(
    'Bring my own data' = 'own_data',
    'Use AnVIL hosted datasets' = 'anvil_data'
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'anvil_data_type',
  label  = 'Do you access raw data (e.g., sequencing reads) or summarized data (e.g., count tables, variant calls, etc.)? (select all that apply)',
  option = c(
    'Raw data' = 'raw',
    'Summarized data' = 'summarized'
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'anvil_data_control',
  label  = 'Do you utilize AnVIL hosted open-access or controlled-access datasets? (select all that apply)',
  option = c(
    'AnVIL hosted open-access datasets' = 'open_access',
    'AnVIL hosted controlled-access datasets' = 'controlled_access'
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'controlled_datasets_use',
  label  = 'Which of the following large, controlled-access datasets do you use on the AnVIL?',
  option = c(
    'Centers for Common Disease Genomics (CCDG)' = 'ccdg',
    'The Centers for Mendelian Genomics (CMG)' = 'cmg',
    'Clinical Sequencing Evidence-Generating Research' = 'cser',
    'Electronic Medical Records and Genomics (eMERGE)' = 'emerge',
    'Gabriella Miller Kids First (GMKF)' = 'gmkf',
    'Genomics Research to Elucidate the Genetics of Rare Diseases (GREGoR)' = 'gregor',
    'The Human Pangenome Reference Consortium (HPRC)' = 'hprc',
    'Population Architecture Using Genomics and Epidemiology (PAGE)' = 'page',
    'Undiagnosed Disease Network (UDN)' = 'udn',
    'Other' = 'other'
  )
)

sd_question(
  type  = 'text',
  id    = 'controlled_datasets_use_other',
  label = 'What "Other" large, controlled-access datasets do you use on the AnVIL?'
)

sd_question(
  type = 'mc',
  id = 'services_use',
  label = 'Do you use data services (e.g., All of Us + AnVIL Imputation)?',
  option = c(
    'Yes' = 1,
    'No' = 0
  )
)

sd_question(
  type = 'mc',
  id   = 'analyses_satisfaction',
  label  = 'How satisfied are you with running analyses on AnVIL?',
  option = c(
    'Very dissatisfied' = 1,
    'Dissatisfied' = 2,
    'Neutral' = 3,
    'Satisfied' = 4,
    'Very satisfied' = 5
  )
)

sd_question( ## Rephrase?
  type   = 'textarea',
  id     = 'what_would_help_services',
  label  = 'What would make AnVIL easier or more useful for **running analyses**?'
)

sd_nav(page_next = 'page7')
```

--- page7

## Specific Use: Group supervision

```{r}

sd_question(
  type   = 'mc',
  id     = 'use_supervise',
  label  = 'Do you supervise (e.g., plan and monitor) the use of the AnVIL platform by others rather than only running analyses or submitting data yourself?',
  option = c(
    'Yes' = 1,
    'No' = 0
  )
)

sd_question(
  type   = 'matrix',
  id     = 'use_supervise_questions',
  label  = 'How much do you agree or disagree with the following statements about AnVIL?',
  row = c(
    'AnVIL helps my team work more efficiently' = 'use_supervise_efficiency',
    'AnVIL helps my team collaborate securely' = 'use_supervise_collab_secure',
    'AnVIL provides resources my team would not otherwise have access to' = 'supervise_provide_resources'
  ),
  option = c(
    'Strongly disagree' = 1,
    'Somewhat disagree' = 2,
    'Neither agree nor disagree' = 3,
    'Somewhat agree' = 4,
    'Strongly agree' = 5
  )
)

sd_question(
  type = 'mc',
  id   = 'use_supervise_satisfaction',
  label  = 'How satisfied are you with supervising others on AnVIL?',
  option = c(
    'Very dissatisfied' = 1,
    'Dissatisfied' = 2,
    'Neutral' = 3,
    'Satisfied' = 4,
    'Very satisfied' = 5
  )
)

sd_question( ## Rephrase?
  type   = 'textarea',
  id     = 'what_would_help_supervise',
  label  = 'What would make AnVIL easier or more useful for **supervising others**?'
)

sd_nav(page_next = 'page8')
```

--- page8

## Specific Use: Educational support

```{r}

sd_question(
  type   = 'mc',
  id     = 'use_ed',
  label  = 'Do you use the AnVIL platform for training or courses that you are leading?',
  option = c(
    'Yes' = 1,
    'No' = 0
  )
)

sd_question(
  type = 'mc',
  id   = 'use_ed_satisfaction',
  label  = 'How satisfied are you with training or leading courses on AnVIL?',
  option = c(
    'Very dissatisfied' = 1,
    'Dissatisfied' = 2,
    'Neutral' = 3,
    'Satisfied' = 4,
    'Very satisfied' = 5
  )
)

sd_question( ## Rephrase?
  type   = 'textarea',
  id     = 'what_would_help_ed',
  label  = 'What would make AnVIL easier or more useful for **training or leading courses**?'
)

sd_nav(page_next = 'page9')

```

--- page9

## Training needs

```{r}

sd_question(
  type   = 'mc',
  id     = 'training_need',
  label  = 'How necessary, if at all, is up-to-date, formal support (e.g., documentation, training, support forum) for your continued and effective use of the AnVIL Platform?',
  option = c(
    '1: Extremely necessary' = 1,
    '2' = 2,
    '3: Neither necessary or unnecessary' = 3,
    '4' = 4,
    '5: Extremely unnecessary' = 5
  )
)

sd_question(
  type   = 'mc',
  id     = 'confident_find_help',
  label  = 'Do you feel confident that you would know where to look to find help?',
  option = c(
    '5: Yes, extremely confident' = 5,
    '4' = 4,
    '3: Neither confident or unconfident' = 3,
    '2' = 2,
    '1: No, extremely unconfident' = 1
  )
)

sd_question(
  type   = 'mc',
  id     = 'demos',
  label  = 'Have you attended a monthly AnVIL Demo?',
  option = c(
    'Yes, multiple' = 'multiple',
    'Yes, one'      = 'one',
    'Not yet, but am registered to' = 'registered',
    'No, but aware of' = 'aware',
    'No, did not know of' = 'unaware'
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'support_forum',
  label  = 'Have you ever read or posted in our AnVIL Support Forum? (select all that apply)',
  option = c(
    "Read through others' posts" = 'read_posts',
    'Posted in' = 'posted',
    "Answered someone's post" = 'answered_post',
    'No, but aware of' = 'aware',
    'No, did not know of' = 'unaware'
  )
)

sd_question(
  type   = 'matrix',
  id     = 'preferred_learning',
  label  = 'Please rank your preferred methods of learning for the AnVIL platform.',
  row    = c(
    'Video tutorials' = 'video',
    'Guided documentation' = 'docs',
    'Live Demos' = 'demos',
    'Workshops' = 'workshops',
    'Support forum' = 'forum',
    'Office hours' = 'office_hours',
    'Other' = 'other'
  ),
  option = c(
    '1 (Most preferred in this list)' = 1,
    '2' = 2,
    '3' = 3,
    '4' = 4,
    '5' = 5,
    '6' = 6,
    '7 (Least preferred in this list)' = 7
  )
)

sd_question(
  type   = 'text',
  id     = 'preferred_learning_other_specify',
  label  = 'What "Other" methods of learning do you prefer?'
)

sd_nav(page_next = 'end')

```

--- end

Thank you for your responses!

```{r}
sd_close()
```
